Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-11-22 2017-Xudong-SMT/checker.tex
Update the checker.tex.
Modify the content after the skype on Nov.21st.

\begin{document}
\section{Type system}
The SMT solver Z3 already has conservative type rules and checks type safety in Horn logic. When translating the pNets into SMT-LIB language, pNets should also make sure that
the term matching other term in SMT-LIB language will be correct in type checking. In next two section, we give out the presentation of the pNets and the type rules of them to ensure the type safety. 
\subsection{Algebra Presentation}
We have a set of basic algebra presentation for the pNet, including three basic sorts $Bool$, $Action$ and $Int$ and their own operators(constants as operators with no argument).
\begin{table}\caption{\leftline{Algebra Presentation}}
	\begin{tabular}{p{4cm}p{8cm}}
		\hline\specialrule{0em}{1pt}{1pt}
		Sort & Operator \\\specialrule{0em}{1pt}{1pt}
		\hdashline\specialrule{0em}{3pt}{3pt}
		Bool    			& $=,\ \ne,\ \land,\ \lor,\ \texttt{true},\ \texttt{false}$ 								\\\specialrule{0em}{1pt}{1pt}
		Action 			& $=,\ \ne,\ \texttt{FUN}$ 																	\\\specialrule{0em}{1pt}{1pt}
		Int 				& $=,\ \ne,\ - \texttt{(unary)},\ +,\ - \texttt{(binary)},\ \times,\ \div,\ \texttt{Nat}$ 			\\\specialrule{0em}{1pt}{1pt}
		\hline
	\end{tabular}
\end{table}

@@

\begin{table}\caption{\leftline{Type Rules for Open pNets}}
	\begin{tabular}{p{5cm}p{5cm}p{2.5cm}}
		\hline\specialrule{0em}{3pt}{3pt}
		(Env $\varnothing$) 								
		& 										
		&					\\\specialrule{0em}{1pt}{1pt}
            $\dfrac{ }{\varnothing \vdash \diamond}$			
            & %$\dfrac{\Gamma \vdash A ~~ x\ }{\varnothing \vdash \diamond}$
            &					\\\specialrule{0em}{3pt}{3pt}
		(Type Bool) 										
		&(Type Action) 						
		&(Type Int)			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash Bool~~\Gamma \vdash \diamond}{\mathcal{P},\Gamma \vdash Bool}$ 
		& $\dfrac{\mathcal{P} \vdash Action~~\Gamma \vdash \diamond}{\mathcal{P},\Gamma \vdash Action}$ 
		& $\dfrac{\mathcal{P} \vdash Int~~\Gamma \vdash \diamond}{\mathcal{P},\Gamma \vdash Int}$        \\\specialrule{0em}{3pt}{3pt}
		(Var x) 										
		& 						
		&			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash A~~\Gamma \vdash x:A}{\mathcal{P},\Gamma \vdash x:A}$ 
		&  
		&       		\\\specialrule{0em}{5pt}{5pt}
		(Expr $\land$)								
		&					
		& 			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash \land :: Bool, Bool \rightarrow Bool ~~\Gamma \vdash x_1:Bool ~~\Gamma \vdash x_2:Bool}{\mathcal{P},\Gamma \vdash x_1 \land x_2:Bool}$ 
		& 
		&       		\\\specialrule{0em}{5pt}{5pt}
		(Expr $\lor$)							
		&					
		& 			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash \lor :: Bool, Bool \rightarrow Bool ~~\Gamma \vdash x_1:Bool ~~\Gamma \vdash x_2:Bool}{\mathcal{P},\Gamma \vdash x_1 \lor x_2:Bool}$ 
		& 
		&       		\\\specialrule{0em}{5pt}{5pt}
		(Expr +)							
		&					
		& 			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash + :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1 + x_2:Int}$ 
		& 
		&       		\\\specialrule{0em}{5pt}{5pt}
		(Expr $\times$)							
		&					
		& 			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash \times :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1 \times x_2:Int}$ 
		& 
		&       		\\\specialrule{0em}{5pt}{5pt}
		(Expr $\div$)							
		&					
		& 			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash \div :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1 \div x_2:Int}$ 
		& 
		&       		\\\specialrule{0em}{5pt}{5pt}
		(Overloading)							
		&					
		& 			\\\specialrule{0em}{3pt}{3pt}
		(Overload =)							
		&					
		& 			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash A ~~\mathcal{P} \vdash = :: A, A \rightarrow Bool ~~\Gamma \vdash x_1:A ~~\Gamma \vdash x_2:A}{\mathcal{P},\Gamma \vdash x_1 = x_2:Bool}$ 
		& 
		&       		\\\specialrule{0em}{5pt}{5pt}
		(Overload $\ne$)							
		&					
		& 			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash A ~~\mathcal{P} \vdash \ne :: A, A \rightarrow Bool ~~\Gamma \vdash x_1:A ~~\Gamma \vdash x_2:A}{\mathcal{P},\Gamma \vdash x_1 \ne x_2:Bool}$ 
		& 
		&       		\\\specialrule{0em}{5pt}{5pt}
		(Polymorphism)							
		&					
		& 			\\\specialrule{0em}{3pt}{3pt}
		(Poly -)							
		&					
		& 			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash - :: Int \rightarrow Int ~~\Gamma \vdash x:Int}{\mathcal{P},\Gamma \vdash -x:Int}$  
		&$\dfrac{\mathcal{P} \vdash - :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1-x_2:Int}$ 
		&       		\\\specialrule{0em}{5pt}{5pt}
		(Poly $\texttt{FUN}$)							
		&					
		& 			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash \texttt{FUN} :: A_1,...,A_n \rightarrow Action ~~\mathcal{P} \vdash A_1~~...~~\mathcal{P} \vdash A_n ~~\Gamma \vdash x_1:A_1~~...~~\Gamma \vdash x_n:A_n}{\mathcal{P},\Gamma \vdash \texttt{FUN}(x_1,...,x_n):Action}$ 
		& 
		&			\\
		\specialrule{0em}{5pt}{5pt}\hline
	\end{tabular}
\end{table}

>>>>

\begin{document}
\section{Type system}
The SMT solver Z3 already has conservative type rules and checks type safety in Horn logic. When translating the pNets into SMT-LIB language, pNets should also make sure that
the term matching other term in SMT-LIB language will be correct in type checking. In next two section, we give out the presentation of the pNets and the type rules of them to ensure the type safety. 
\subsection{Algebra Presentation}
We have a set of basic algebra presentation for the pNet, including three basic sorts $Bool$, $Action$ and $Int$ and their own operators(constants as operators with no argument).
\begin{table}\caption{\leftline{Algebra Presentation}}
	\begin{tabular}{p{4cm}p{8cm}}
		\hline\specialrule{0em}{1pt}{1pt}
		Sort & Operator \\\specialrule{0em}{1pt}{1pt}
		\hdashline\specialrule{0em}{3pt}{3pt}
		Bool    			& $=,\ \ne,\ \land,\ \lor,\ \texttt{true},\ \texttt{false},\ \texttt{FUN}$ 								\\\specialrule{0em}{1pt}{1pt}
		Action 			& $=,\ \ne,\ \texttt{FUN}$ 																	\\\specialrule{0em}{1pt}{1pt}
		Int 				& $=,\ \ne,\ - \texttt{(unary)},\ +,\ - \texttt{(binary)},\ \times,\ \div,\ \texttt{Nat},\ \texttt{FUN}$ 			\\\specialrule{0em}{1pt}{1pt}
		\hline
	\end{tabular}
\end{table}

@@

\begin{table}\caption{\leftline{Type Rules for Open pNets}}
	\begin{tabular}{p{5cm}p{5cm}p{2.5cm}}
		\hline\specialrule{0em}{3pt}{3pt}
		(Env $\varnothing$) 								
		& 										
		&					\\\specialrule{0em}{1pt}{1pt}
            $\dfrac{ }{\varnothing \vdash \diamond}$			
            & %$\dfrac{\Gamma \vdash A ~~ x\ }{\varnothing \vdash \diamond}$
            &					\\\specialrule{0em}{3pt}{3pt}
		(Type Bool) 										
		&(Type Action) 						
		&(Type Int)			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash Bool~~\Gamma \vdash \diamond}{\mathcal{P},\Gamma \vdash Bool}$ 
		& $\dfrac{\mathcal{P} \vdash Action~~\Gamma \vdash \diamond}{\mathcal{P},\Gamma \vdash Action}$ 
		& $\dfrac{\mathcal{P} \vdash Int~~\Gamma \vdash \diamond}{\mathcal{P},\Gamma \vdash Int}$        \\\specialrule{0em}{3pt}{3pt}
		(Var x) 										
		& 						
		&			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash A~~\Gamma \vdash x:A}{\mathcal{P},\Gamma \vdash x:A}$ 
		&  
		&       		\\\specialrule{0em}{5pt}{5pt}
		(Expr Unary)								
		&					
		& 			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash A ~~\mathcal{P} \vdash op :: A \rightarrow A ~~\Gamma \vdash x:A}{\mathcal{P},\Gamma \vdash op~x:A}$ 
		& 
		&       		\\\specialrule{0em}{5pt}{5pt}
		(Expr Binary)							
		&					
		& 			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash A ~~\mathcal{P} \vdash op :: A, A \rightarrow A ~~\Gamma \vdash x_1:A ~~\Gamma \vdash x_2:A}{\mathcal{P},\Gamma \vdash x_1~op~ x_2:A}$ 
		& 
		&       		\\\specialrule{0em}{5pt}{5pt}
%		(Expr +)							
%		&					
%		& 			\\\specialrule{0em}{1pt}{1pt}
%		$\dfrac{\mathcal{P} \vdash + :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1 + x_2:Int}$ 
%		& 
%		&       		\\\specialrule{0em}{5pt}{5pt}
%		(Expr $\times$)							
%		&					
%		& 			\\\specialrule{0em}{1pt}{1pt}
%		$\dfrac{\mathcal{P} \vdash \times :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1 \times x_2:Int}$ 
%		& 
%		&       		\\\specialrule{0em}{5pt}{5pt}
%		(Expr $\div$)							
%		&					
%		& 			\\\specialrule{0em}{1pt}{1pt}
%		$\dfrac{\mathcal{P} \vdash \div :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1 \div x_2:Int}$ 
%		& 
%		&       		\\\specialrule{0em}{5pt}{5pt}
		(Polymorphism)							
		&					
		& 			\\\specialrule{0em}{3pt}{3pt}
		(Poly =)							
		&					
		& 			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash A ~~\mathcal{P} \vdash = :: A, A \rightarrow Bool ~~\Gamma \vdash x_1:A ~~\Gamma \vdash x_2:A}{\mathcal{P},\Gamma \vdash x_1 = x_2:Bool}$ 
		& 
		&       		\\\specialrule{0em}{5pt}{5pt}
		(Poly $\ne$)							
		&					
		& 			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash A ~~\mathcal{P} \vdash \ne :: A, A \rightarrow Bool ~~\Gamma \vdash x_1:A ~~\Gamma \vdash x_2:A}{\mathcal{P},\Gamma \vdash x_1 \ne x_2:Bool}$ 
		& 
		&       		\\\specialrule{0em}{5pt}{5pt}
%		(Poly -)							
%		&					
%		& 			\\\specialrule{0em}{1pt}{1pt}
%		$\dfrac{\mathcal{P} \vdash - :: Int \rightarrow Int ~~\Gamma \vdash x:Int}{\mathcal{P},\Gamma \vdash -x:Int}$  
%		&$\dfrac{\mathcal{P} \vdash - :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1-x_2:Int}$ 
%		&       		\\\specialrule{0em}{5pt}{5pt}
		(Poly $\texttt{FUN}$)							
		&					
		& 			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash \texttt{FUN} :: A_1,...,A_n \rightarrow A ~~\mathcal{P} \vdash A_1~~...~~\mathcal{P} \vdash A_n ~~\mathcal{P} \vdash A ~~\Gamma \vdash x_1:A_1~~...~~\Gamma \vdash x_n:A_n}{\mathcal{P},\Gamma \vdash \texttt{FUN}(x_1,...,x_n):A}$ 
		& 
		&			\\
		\specialrule{0em}{5pt}{5pt}\hline
	\end{tabular}
\end{table}
